### 2015-01-18 src/introduction.Rnw
updates from amin

Finally, with bytecode~\footnote{
A \textit{do faster} approach for eliminating
the compilation step to gain execution speed
} based mutation
engines like PIT~\cite{pitest} and Javalanche~\cite{javalanche},
operators based on source code modification are no longer applicable, and their
equivalents in bytecode need to be identified and compared with other
approaches. A detailed discussion of our approach can be found in
Section~\ref{sec:methodology}.

We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
$312$ Java programs from Github, with size ranging from $50$ to $100,000$
lines (excluding tests), allowing us to draw more widely applicable
statistical inferences.

@@

Section~\ref{sec:related} describes the research in mutation reduction 
strategies. Section~\ref{sec:methodology} discusses the sampling and
operator
selection strategies we study in detail. The analysis is given in
Section~\ref{sec:analysis}, and the results of our
experiment are given in Section~\ref{sec:results}, followed by
detailed discussion of what these results imply in Section
~\ref{sec:discussion}. The specific contributions of this paper are:

@@

>>>>

Finally, with bytecode~\footnote{A \textit{do faster} approach for
eliminating the compilation step to gain execution speed} based mutation
engines such as PIT~\cite{pitest} and Javalanche~\cite{javalanche} becoming
common in both development and research (e.g. \cite{zhang2013ase},
\cite{gopinath2014code}, and \cite{inozemtseva2014coverage}),
operators based on source code modification are no longer directly applicable,
and their equivalents in bytecode need to be identified and compared with other
approaches.

This paper studies different mutant selection strategies on large number of
Java programs using a popular bytecode-based mutation PIT.
We sampled $312$ opensource Java project between $50$ to $100K$ non-comment
lines of code (excluding test cases) from Github and Apache Foundation. This
set of projects include many of popular Java projects that are regualry used in
literature (such as Apache Common Lang, Common Math and Joda Time). For the
mutation analysis of this study, we choose PIT, a fast and easy to use mutation
analysis tool for Java, which has been used by researchers in the
past~\cite{gopinath2014code,inozemtseva2014coverage} for its wide range of
operators.
% Amin: Total lines of code, total number of mutants

For this study, we experimented four classic mutation selection techniques: Constrained \cite{wong1995reducing}, E-       Selective \cite{offutt1996anexperimental}, Javalanche \cite{javalanche} and N-Selection
\cite{offutt1993experimental}, along with two sampling approaches: element based \cite{zhang2013ase} and operator based   sampling \cite{wong1995reducing}. We compare test effectiveness of each of techniques
with pure random sampling. Our results show that in most cases there is no statistically significant benefit for mutation selection techniques. Moreover, in cases with statistically significant benefit, the gain is
so low that is essentially negligible.

\begin{comment}
We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
$312$ Java programs from Github, with size ranging from $50$ to $100,000$
lines (excluding tests), allowing us to draw more widely applicable
statistical inferences.
\end{comment}

@@

The specific contributions of this paper are:

@@

\noindent\textbf{Organization.} Section~\ref{sec:related} describes the
research in mutation reduction strategies. Section~\ref{sec:methodology}
 discusses the sampling and operator
selection strategies we study in detail. The analysis is given in
Section~\ref{sec:analysis}, and the results of our
experiment are given in Section~\ref{sec:results}, followed by
detailed discussion of what these results imply in Section
~\ref{sec:discussion}.
